Lensing

### 2015-02-02 Papers/ms.tex
Put PGM in paper
Blobs

>>>>

\section{The Model}
The surface brightness profile of the source is assumed to be composed of
a sum of a finite number of ``blobs'', or circular basis functions.
The surface brightness of a single blob centered at the origin
is:
\begin{eqnarray}
f(x, y) &=& \left\{
\begin{array}{lr}
\frac{A}{2\pi w^2}\left[1 - \left(\frac{r}{w}\right)^2\right], & r \leq w\\
0, & \textnormal{otherwise}
\end{array}
\right.
\end{eqnarray}
where $r = \sqrt{x^2 + y^2}$, $w$ is the width of the blob, and $A$ is the
total flux of the blob (i.e. the integral of the surface brightness).
These basis functions are faster to evaluate than gaussians, since they do not
contain an exponential function. In addition, the finite support means that
each blob will evaluate to zero over a large fraction of the domain which
confers an additional speed advantage.

\begin{figure*}
\includegraphics{pgm.pdf}
\caption{A probabilistic graphical model (PGM) of the dependence structure
of the prior information.\label{fig:pgm}}
\end{figure*}
